A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-16 draft.tex
Fleshes out cloud possibilities, closes #24

  \item[A container orchestration service]: These services are compatible with {\tt docker-compose}
    files for configuration and provide transparent provisioning. Examples of these
    services are Amazon Elastic Container Service,  Red Hat Openshift
    (which is also open-source), and Marantis Docker Enterprise using Docker Swarm.
    Salza et al. \cite{salza2019speed} tested a variant of this option by using a CoreOs cluster.

@@

%\subsubsection{Setup} % Even if it's a sub-sub section, flesh this out ... - JJ
%\label{setup:local-cloud}

We chose the second option, a container orchestration service. We
deployed the EvoSwarm application in Amazon Elastic Container Service (ECS)
since it needs fewer changes in configuration (from deploying it locally using
{\tt docker-compose}) and it has a lower cost than the Kubernetes
alternative.

We can define an ECS cluster directly on the AWS Elastic Cloud VMs or through the
AWS Fargate service. Fargate is a serverless compute engine for containers that
provides automatic provision and management of AWS ECS resources. With this
service, calculating the cost of execution is simplified because users only
specify the computing units and memory for the application, instead of every
component. However, AWS Fargate is not suited for an experimental setting because
many of the details are out of user control. For this reason, we chose the
alternative of using a cluster of EC2 containers. The drawback is that we need to manually
provision the  EC2 containers, networking, and group permissions for each
experimental setup; for instance, when going from 2 to 8 workers, we need to increase the
number of EC2 instances to meet the required amount of CPU units.

>>>>

  \item[A container orchestration service]: These services are compatible with {\tt docker-compose}
    files for configuration and provide transparent provisioning. Examples of these
    services are Amazon Elastic Container Service,  Red Hat Openshift
    (which is also open source), and Marantis Docker Enterprise using Docker Swarm.
    Salza et al. \cite{salza2019speed} tested a variant of this option by using a CoreOs cluster.

@@

We chose the second option, a container orchestration service. We
deployed the EvoSwarm application in Amazon Elastic Container Service (ECS)
since it needs fewer changes in configuration (from deploying it locally using
{\tt docker-compose}) and it has a lower cost than the Kubernetes
alternative. This does not imply any loss of generality; first,
because it's {\tt docker-compose} compatible, and it can be deployed
in approximately the same way to any of the services, mentioned above,
compatible with it. Since {\tt docker-compose} is open source, it can
be ported to any computing node, and can thus be deployed to any other
cloud service like Azure or Google Cloud Platform. At any rate, please
note that there are several levels of infrastructure programming
here. At the lowest level, we are using docker containers, which are
compatible across a myriad of cloud providers in one way or other. At
the next level, we are using a container composition technology that
is also standard, {\tt docker compose}, once again compatible across
any platform that can host that kind of service. There's, however, a
final, platform-specific, infrastructure definition that will have to
vary across any public or private cloud platform that we are using,
and that will tap the cloud provider API. These changes, however, are
usually minimal, and can also be done through the CLI or using the web
console.

For instance, we can define an ECS cluster directly on the AWS Elastic Cloud VMs or through the
AWS Fargate service. Fargate is a serverless compute engine for containers that
provides automatic provision and management of AWS ECS resources. With this
service, calculating the cost of execution is simplified because users only
specify the computing units and memory for the application, instead of every
component. However, AWS Fargate is not suited for an experimental setting because
many of the details are out of user control. For this reason, we chose the
alternative of using a cluster of EC2 containers. The drawback is that we need to manually
provision the  EC2 containers, networking, and group permissions for each
experimental setup; for instance, when going from 2 to 8 workers, we need to increase the
number of EC2 instances to meet the required amount of CPU units.
